Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-06 ms.tex
updating figures.

The left panel of Figure \ref{fig:miller} is calculated assuming a
constant low value for the radiative efficiency $\epsilon_X = 10^{-4}$
typical of those estimated for low luminosity AGN (e.g.,
\citealt{Ho:2009a}), while the right panel luminosities are calculated
instead assuming an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm
  edd}$ that depends on the Eddington ratio as predicted by some
models for radiatively inefficient accretion flows
(\citealt{Narayan&Yi95}; \citealt{Narayan+98}).  Shown for comparison
are the X-ray measurements (green stars) and upper limits (gray
triangles) of early-type galaxies compiled by \citet{Miller+15}
(cf.~\citealt{Gallo+10}).  A green line shows the best power-law fit
to the X-ray luminosity from \citet{Miller+15}, given by $\langle
L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$ with $\alpha = -0.2$ (see also
\citep{Zhang+09, Pellegrini10, Gallo+10} for similar conclusions).
Yellow, teal, and red lines show the maximum accretion rates,
respectively, for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]),
as set by SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]), and as allowed by
Compton heating feedback (eq.~[\ref{eq:MdotC}]).

@@

A more readily addressable test is whether a steady-state accretion
picture is capable of explaining the large scatter of typically 2-3
orders of magnitude in the observed distribution of $L_{X}/L_{\rm
  edd}$ at fixed $M_{\bullet}$.  Scatter is expected to result from at
least two effects: (1) the order of magnitude difference between
$\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$
(Fig.~\ref{fig:bh_growth}) leads to a similar scatter of $\dot{M}$ due
to the variation in the Nuker stellar density profile $\Gamma$ at
fixed $M_{\bullet}$; (2) the strong sensitivity of the accretion rate
to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in
combination with the significant dependence of $v_w$ on stochastic
intermittency in the star formation history (Fig.~NICK).  The
combination of (1) and (2) is capable of explaining much of the
observed sample, especially considering that scatter in $L_{\rm X}$
due to variations in $\dot{M}$ is exacerbated by the expectation that
$\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows.

>>>>

The left panel of Figure \ref{fig:miller} is calculated assuming a
constant low value for the radiative efficiency $\epsilon_X = 10^{-4}$
typical of those estimated for low luminosity AGN (e.g.,
\citealt{Ho:2009a}), while the right panel luminosities are calculated
instead assuming an efficiency of $\epsilon_X= 10 \dot{M}/\dot{M}_{\rm
  edd}$ that depends on the Eddington ratio as predicted by some
models for radiatively inefficient accretion flows
(\citealt{Narayan&Yi95}; \citealt{Narayan+98}).  Shown for comparison
are the X-ray measurements (green stars) and upper limits (gray
triangles) of early-type galaxies compiled by \citet{Miller+15}
(cf.~\citealt{Gallo+10}).  A green line shows the best power-law fit
to the X-ray luminosity from \citet{Miller+15}, given by $\langle
L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$ with $\alpha = -0.2$ (see also
\citep{Zhang+09, Pellegrini10, Gallo+10} for similar conclusions).
Yellow, teal, and red lines show the maximum accretion rates,
respectively, for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]),
as set by SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]), and as allowed by
Compton heating feedback (eq.~[\ref{eq:MdotC}]).

@@

A more readily addressable test is whether a steady-state accretion
picture is capable of explaining the large scatter of typically 2-3
orders of magnitude in the observed distribution of $L_{X}/L_{\rm
  edd}$ at fixed $M_{\bullet}$.  Scatter is expected to result from at
least two effects: (1) the order of magnitude difference between
$\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$
(Fig.~\ref{fig:bh_growth}) leads to a similar scatter of $\dot{M}$ due
to the variation in the Nuker stellar density profile $\Gamma$ at
fixed $M_{\bullet}$; (2) the strong sensitivity of the accretion rate
to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in
combination with the significant dependence of $v_w$ on stochastic
intermittency in the star formation history (Fig.~NICK).  The
combination of (1) and (2) is capable of explaining much of the
observed sample, especially considering that scatter in $L_{\rm X}$
due to variations in $\dot{M}$ is exacerbated by the expectation that
$\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows {\bf
  AG Challenge: Scatter in L_X is similar for cores and cusps in Perllegrini}.
